Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: template figures

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/ssgb_posteriors.pdf}
\caption{Template.}
\label{fig:sGB_exec_sum}
\end{figure}

>>>>

\subsubsection{Stacking posteriors}
\label{sec:stack}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/edgb_posteriors_combined.pdf}
\caption{(Color online).~Posterior distribution function in EdGB gravity
for the coupling constant $\ell_{\rm GB}$ for GW150914 (top panel), GW200129 (middle panel)
and combined events (bottom panel).
%
In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
in spin QNM correction.}
\label{fig:sGB_exec_sum}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/edgb_cdf_varying_threshold.pdf}
\caption{(Color online).~The cumulative distribution function evaluated at the
threshold $T(\varepsilon;\, m)$ EdGB gravity as a function of the parameter
$\varepsilon$ for both (blue curves) $m = m_2$, the secondary's source
mass, and (orange curves) $m = M_{f}$, the remnant's source mass, without
(solid curve) and with (dashed curves) linear in spin QNM corrections. The
horizontal lines lay at 0.68 and 0.90.
}
\label{fig:dcs_cdf}
\end{figure}
